The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free eLearning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2009-07-09 script/en/chapters/numbertheory.tex
sync de hypertarget name change to en

{\bf Example 1:} \\
The following table\footnote{%
See \hyperlink{AppArith3a}{Appendix E of this chapter} for the source
code to generate the table using Sage.} 
shows the values $a^i$ mod $11$ for the exponents $i = 1, 2, \cdots, 10$ and for the bases 
$a =  1, 2, \cdots, 10$ as well as the resulting value $ord_{11}(a)$ for each $a$:

@@

\hypertarget{AppArith3a}{}
\subsubsection*{Multiplicative order}

@@

\subsection*{Primitive roots}

>>>>

{\bf Example 1:} \\
The following table\footnote{%
See \hyperlink{AppArith3a1}{Appendix E of this chapter} for the source
code to generate the table using Sage.} 
shows the values $a^i$ mod $11$ for the exponents $i = 1, 2, \cdots, 10$ and for the bases 
$a =  1, 2, \cdots, 10$ as well as the resulting value $ord_{11}(a)$ for each $a$:

@@

\hypertarget{AppArith3a1}{}
\subsection*{Multiplicative order}

@@

\hypertarget{AppArith3a2}{}
\subsection*{Primitive roots}
